### 2021-03-16 README.Rmd
Added zonetosau for summary plots. MSE functioning correctly.

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(ddir,"aMSE/data-raw/","TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"control2.csv",cleanslate = TRUE) # normally would read in a file
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,sigR=1e-08,sigB=1e-08)
# save conditioned results -----------------------------------------------------
save(zoneDD,file=filenametopath(rundir,"zoneDD.RData"))
# Illustrate productivity
propD <- getzoneprops(zoneC,zoneDD,glb,year=47)
addtable(round(t(propD),4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[45:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last three years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
cmcda <- mcdahcr(arrce=condC$histCE,hsargs=hsargs,
                 yearnames=rownames(condC$histCE),saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
#out <- prepareprojection(projC,zoneC,glb,zoneDD,ctrl,multTAC)
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            zoneDD=zoneDD,ctrl=ctrl,varyrs=6,
                            multTAC=multTAC,lastsigR = 0.25)

zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP

@@

>>>>

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(ddir,"aMSE/data-raw/","TasmanianHS.R"))
# generate equilibrium zone ----------------------------------------------------
starttime2 <- (Sys.time())
zone <- makeequilzone(rundir,"control2.csv",cleanslate = TRUE) # normally would read in a file
equiltime <- (Sys.time()); print(equiltime - starttime2)
# declare main objects ---------------------------------------------------------
glb <- zone$glb
ctrl <- zone$ctrl
zone1 <- zone$zone1
projC <- zone1$projC
condC <- zone1$condC
zoneC <- zone$zoneC
zoneD <- zone$zoneD
product <- zone$product
# add some tables and plots into rundir
biology_plots(rundir, glb, zoneC)
plotproductivity(rundir,product,glb)
numbersatsize(rundir, glb, zoneD)
# Condition on Fishery ---------------------------------------------------------
zoneDD <- dohistoricC(zoneD,zoneC,glob=glb,condC,sigR=1e-08,sigB=1e-08)
# save conditioned results -----------------------------------------------------
save(zoneDD,file=filenametopath(rundir,"zoneDD.RData"))
# Illustrate productivity
propD <- getzoneprops(zoneC,zoneDD,glb,year=47)
addtable(round(t(propD),4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[45:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last three years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
cmcda <- mcdahcr(arrce=condC$histCE,hsargs=hsargs,
                 yearnames=rownames(condC$histCE),saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
#out <- prepareprojection(projC,zoneC,glb,zoneDD,ctrl,multTAC)
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            zoneDD=zoneDD,ctrl=ctrl,varyrs=8,
                            multTAC=multTAC,lastsigR = 0.25)

zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

@@

After running the whole, even if you do not generate the results webpage, you could also try:

```{r combined_plot, fig.height=7, fig.width=6 }
B0 <- getvar(zoneC,"B0")
ExB0 <- getvar(zoneC,"ExB0")

zoneDsau <- zonetosau(zoneDDR,glb,B0,ExB0)
zonePsau <- zonetosau(zoneDP,glb,B0,ExB0)

nsau <- glb$nSAU
label <- glb$saunames
CIprobs <- c(0.05,0.5,0.95)
sauCI <- vector("list",nsau)
postyrs <- ctrl$projection
startyr <- 40

invar <- "cpue"
prerep <- zoneDsau[[invar]]
allrep <- zonePsau[[invar]]
preyrs <- dim(prerep)[1]
allyrs <- preyrs + postyrs
reps <- dim(prerep)[3]

plotprep(width=8, height=8,newdev=FALSE)
parset(plots=c(4,2))
for (sau in 1:nsau) {
  ymax <- getmax(rbind(prerep[startyr:preyrs,sau,],allrep[,sau,]))
  traj <- c(prerep[startyr:preyrs,sau,1],allrep[,sau,1])
  plot(startyr:allyrs,traj,type="l",lwd=1,col="grey",panel.first=grid(),
       ylab=paste0(invar,"  ",label[sau]),ylim=c(0,ymax))
  for (i in 2:reps)
    lines(startyr:allyrs,c(prerep[startyr:preyrs,sau,i],allrep[,sau,i]),lwd=1,col="grey")
  CI <- apply(allrep[,sau,],1,quantile,probs=CIprobs)
  lines((preyrs+1):allyrs,CI[2,],lwd=2,col=4)
  lines((preyrs+1):allyrs,CI[1,],lwd=1,col=2)
  lines((preyrs+1):allyrs,CI[3,],lwd=1,col=2)
  sauCI[[sau]] <- CI
  abline(v=(preyrs+0.5),col=2)
 if (invar == "cpue") abline(h=150,col=2)
}
